---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AnalyzeResp 

<!-- badges: start -->
[![R-CMD-check](https://github.com/kraskura/AnalyzeResp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kraskura/AnalyzeResp/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This project is in transition to update. The older version is documented here: https://kraskura.github.io/AnalyzeResp_0/
Please note, the older version will not be changed or improved. 


## Installation:

The development version of AnalyzeResp can be installed from [GitHub](https://github.com/) with:

``` r
install.packages("devtools") # if devtools is not installed
devtools::install_github("kraskura/AnalyzeResp")
library(AnalyzeResp)

```

## What has changed since the last version:

- The folder names and process
- Multiple SMR and SDA files combine on the spot 
- Convert units in the convert text function
- The 'csv_files' folder is 'outside'
- SMR inventory lives 'outside' in the main wd (as set at the start)
- Dont' need to reset wd 
- Names of the functions

## To do list: 

- Clean the code and get syntax under control. (some arguments have "." in names, while some have "_" in their names). Carryover of old not good practices of coding 
- Make sure the imported libraries load 
- Rework the manual and instructions 
- Rework an example code with the following scenarios 
  + One files and multiple (glued files) 
  + Various background strategies (one back prior, only back pre, etc)
- Document the independent sliding window analysis
- Use this for Loligo respos (Witrox file recorded files)
- Revise exported data files and make sure each column of data is necessary, revise accordingly. 
- Improve and label plots
- Revise and delete the out-commented unused code
- Use lintr to clean up old mess

```{r example}

```

