---
title: "Example code to analyze respirometry data"
output:
  html_document:
    df_print: paged
---
### Step 1. install and load package
### 1. Loading Analyze Resp
 
```{r messages = F, warning=F}
# install.packages("devtools") # if devtools is not installed
# ("AnalyzeResp")
# install.packages("devtools")
# library(devtools)
devtools::install_github("kraskura/AnalyzeResp", force = TRUE)
library(AnalyzeResp)
# other libraries, dependencies:
library(pacman)
p_load(stats, ggplot2, scales,grDevices,graphics,utils,dplyr,magrittr, stringr,pryr,tidyr,plotrix,mclust,gridExtra,DescTools,rMR, tidyr)

```

* **Error**: *namespace ‘rlang’ 1.0.6 is already loaded, but >= 1.1.0 is required*
# `remove.packages("rlang")` or any package 

********************************************
**Setup 1**

Have a folder locally that is dedicated to data analysis. All raw text files, or excel files are located directly in this folder (not in sub-folders). Then begin analysis as described in the steps below.  

********************************************

### 2. Create all working directories as needed 
Note it creates csv_files in the local directory now 

```{r messages = F, warning=F}
organizeAnalysisLocally()
# selected option 4 for full analysis (MMR, SMR, AS, recovery)
# list.files() # checks what is directories are present in the local dir(project dir)

```

### 4. convert from txt to csv

```{r messages = F, warning=F}

textFileConvert(txt_file = "apr13_2023_box1_crayfish_tap_test1_mmr.csv",
                local_path = FALSE,
                type_file = "Witrox_2023",
                N_Ch = 4,
                nrowSkip = 21, # witrox
                convert_units = TRUE,
                units_from = "pct", # units of oxygen measured 
                units_to = "mg/L",
                salinity = 0,
                atm_pressure = 1)

textFileConvert(txt_file = "apr13_2023_box1_crayfish_tap_test1_smr.csv",
                local_path = FALSE,
                type_file = "Witrox_2023",
                N_Ch = 4,
                nrowSkip = 21, # witrox
                convert_units = T,
                units_from = "pct",
                units_to = "mg/L",
                salinity = 0,
                atm_pressure = 1)

textFileConvert(txt_file = "apr13_2023_box1_crayfish_tap_test1_smr2.csv",
                local_path = FALSE,
                type_file = "Witrox_2023",
                N_Ch = 4,
                nrowSkip = 21, # witrox
                convert_units = T,
                units_from = "pct",
                units_to = "mg/L",
                salinity = 0,
                atm_pressure = 1)

```


### 5. Run MMR file

```{r messages = F, warning=F}

MMR(data.MMR = "apr13_2023_box1_crayfish_tap_test1_mmr.csv",
    cycles = 4, # add an error message on this - the number of cyclces and the #s must match below
    cycle_start = c(0, 12.5, 24, 35), # (fish1, fish2, )
    cycle_end = c(10, 21, 31, 45),
    mmr_Ch1 = 1,
    mmr_Ch2 = 2,
    mmr_Ch3 = 3,
    mmr_Ch4 = 4, # add an error message on this(wrong cycle)
    N_Ch = 4,
    local_path = FALSE,
    date_format = c("%m/%d/%Y %H:%M:%S", "GMT"))


```

### 6. Run SMR file

```{r}

SMR(data = "apr13_2023_box1_crayfish_tap_test1_smr2.csv",
    cycle_end = 20,
    cycle_start = 5,
    first_cycle = "flush",
    chop_start = 30/60,
    chop_end = 30/60,
    date_format = c("%m/%d/%Y %H:%M:%S", "GMT"), # PDT
    local_path = FALSE,
    background_data = FALSE,
    sda_data = FALSE)


```

### 7. Complete run of AS, MMR, SMR and recovery analysis 

```{r}

# relying on defaults
MMR_SMR_AS_EPOC(data.MMR = "apr13_2023_box1_crayfish_tap_test1_mmr_analyzed.csv",
                data.SMR = "apr13_2023_box1_crayfish_tap_test1_smr2_analyzed.csv",
                AnimalID = c("ID7","ID8","ID9","ID10"),
                BW.animal = c(0.14,0.14,0.14,0.14),
                resp.V = c(0.930, 0.930, 0.930, 0.930),
                r2_threshold_smr = 0.9,
                r2_threshold_mmr = 0.9,
                min_length_mmr = 120,
                local_path = F,
                background_prior = "apr13_2023_box1_crayfish_tap_test1_mmr_back_prior_analyzed.csv",
                background_post = "apr13_2023_box1_crayfish_tap_test1_smr2_analyzed.csv",
                MLND = F)


```

### 8. SDA 

```{r}



```
 
 